ONLINE APPENDIX: The controlled choice design and private paternalism in pawnshop borrowing

### 2024-05-21 ECTA submission/OA_ecta.tex
ecta submission

\title{The controlled choice design and private paternalism in pawnshop borrowing - ONLINE APPENDIX}
\runtitle{The controlled choice design and private paternalism}

@@

\section{Treatment Explanation Materials and Pictures}

\subsection{Materials}

\begin{figure}[!htb]
     \caption{Contract Terms Summary}
    \label{PaperSlip}
    \begin{center}
        \includegraphics[width=0.7\textwidth]{Figuras/TicketLenderP.png}
    \end{center}
    \legend{We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity). We want to highlight the salience of some items. First the title clearly indicated which contract the client has (arrow 1). Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 2\% of the value of the monthly payment (arrow 2). Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.}
\end{figure}

\begin{figure}[!htb]
     \caption{Explanatory Material}
    \label{ExplanatoryMaterial}
    \begin{center}
    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.7\textwidth]{Figuras/micas.pdf}
    \end{subfigure}
    \end{center}
    \legend{ This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.}
\end{figure}

\subsection{Pictures}

\begin{figure}[!htb]
     \caption{Some Pawnshops}
    \label{PawnshopPicture}
    \begin{center}
    \begin{subfigure}{0.405\textwidth}
    \caption{Appraiser/tellers inside a pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio9_.png}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio11_.png}
    \end{subfigure}

        \vspace{3ex}

    \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
    \end{subfigure}
    \begin{subfigure}{0.415\textwidth}
    \caption{Lost pawns which are for sale}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
    \end{subfigure}
    \end{center}
   \legend{ This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. }
\end{figure}

\begin{figure}[!htb]
     \caption{Gold buyers next to pawnshops}
    \label{GoldBuyers}
    \begin{center}
    \begin{subfigure}{.49\textwidth}
    \caption{Gold buyer next to pawnshop 1}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio7_.png}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
    \caption{Gold buyer next to pawnshop 1}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio8_.png}
    \end{subfigure}
       \vspace{3ex}

    \end{center}
    \legend{  This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. }
\end{figure}

\subsection{Descriptives consistent with overconfidence}

\vspace{.2in}
\begin{figure}[!htb]
    \caption{Behavior of borrowers who lost their pawn}
    \label{proxy_naive}
    \begin{center}
    \begin{subfigure}{0.40\textwidth}
        \caption{Elapsed days to first payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.40\textwidth}
        \caption{Elapsed days to last payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
    \end{subfigure}
        \begin{subfigure}{0.40\textwidth}
        \caption{Payments as \% of loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.40\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
    \end{subfigure}
    \end{center}
       \legend{ This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn. Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment. Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan. This amounts to starting a new loan with the same conditions and same pawn. Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.}
      %\textit{Do file: }  \texttt{hist\_den\_default.do}
\end{figure}

\section{Internal Validity}

\subsection{Survey}   \label{app:survey_data}

We now present analysis of the extent to which the survey-responding sample is representative and balanced.
Table \ref{SS_cond_survet} presents information about survey non-response.
Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to at least one survey question.
The p-values in the fourth column are for the F-test of no difference of means across treatment arms. 
Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rates across treatment arms. 
This panel uses data from participants who answered at least one survey question and went on to pawn on the same day as their survey response.
From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are likewise stable across treatment arms.
Table \ref{TUT_cond_survet} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
In each row, column (1) presents the full-sample TUT estimate and standard error while the remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex. 
As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
In exercises that rely on a single survey question, we use data for every borrower who answered that question.
In the random forest exercises described below, we use data for every borrower who answered at least one survey question.

\begin{table}[!htb]
\caption{Baseline survey questions (translated to English)}
\label{baseline_survey}
\begin{center}
\scriptsize{\input{./Tables/transcribed.tex}}
\end{center}
\legend{ Translation of the baseline questionnaire.}
\end{table}

\begin{figure}[!htb]
     \caption{Box-plot across arms}
    \label{boxplot_attrition}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
    \caption{Number of pawns}
        \centering
        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
    \caption{Number of borrowers}
        \centering
        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
    \end{subfigure}
    \end{center}
    \legend{ This figure presents box-plot for the number of pawns and borrowers per branch-day across different arms. The solid black line represent the median, while the gray line represent the mean. The dots on top of the box-plot represent an implicit CDF. }
\end{figure}

\begin{table}[!htb]
\caption{Balance conditional on survey response and question-by-question response rates by treatment arm}
\label{SS_cond_survet}
\begin{center}
\scriptsize{\input{./Tables/SS_cond_survey.tex}}
\end{center}
\legend{ Panel A of this table presents the same information as Panel A of Table \ref{SS}, but restricts attention to the subsample of borrowers who answered at least one question in our baseline survey. Conditional on survey response, loan amount and weekday are balanced across treatment arms. Panel B presents response rates to each individual survey question across treatment arms, along with p-values for the F-test of no difference in response rates across survey arms. This panel uses data for borrowers who pawned on the same day as their survey response. }

%\textit{Do file: } \texttt{ss\_att.do}
\end{table}

\begin{landscape}
\begin{table}[!htb]
\caption{Survey Non-response: TUT estimates for respondents to each survey question.}
\label{TUT_cond_survet}
\begin{center}
\scriptsize{\input{./Tables/tut_cond_survey.tex}}
\end{center}
\legend{ Some borrowers did not respond to our survey; others only completed part of the survey.
This table computes the TUT effect for a number of sub-groups by survey response, and compares them against the overall TUT effect.
The top panel uses financial cost as the outcome variable, while the bottom panel uses APR.
Each group is defined by the borrowers who responded to a particular \emph{subset} of the survey questions. 
For example, column (4) computes TUT effects for the subgroup of borrowers who responded to the two questions needed to compute our measure of present bias, while column (8) computes the TUT for the subgroup of borrowers who provided their age.
The bottom row of the table counts the number of borrowers in each category.
TUT estimates are quite stable across sub-groups and generally similar to the full-sample estimates.
Because standard errors increase as sample size falls, some of the sub-group estimates are not statistically significant.}
%\textit{Do file: } \texttt{tut_cond_survey.do}
\end{table}
\end{landscape}

\section{Main treatment effects: Additional material}

\begin{landscape}
\subsection{Multiple loans}

\begin{table}[!htb]
\caption{Multiple-loans robustness check}
\label{multiple_loans}
\begin{center}
\scriptsize{\input{./Tables/multiple_loans.tex}}
\end{center}
 \legend{ An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.  43\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.  The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure (ITT) \citep{cullen2006effect, abdulkadirouglu2011accountability}.\\
 This table provides robustness for our main results for different ways to handling the multiplicity of loans. Columns 1-4 repeat the main analysis of financial cost and APR using the baseline approach from our main results,i.e. it only considers the first visit, while allowing multiple loans for the same-day. Columns 5-8 considers all loans including dummies for the order of pawns for an individual, essentially making the identification within-order.  Columns 9-12 pursue the ITT strategy of always assigning the first treatment status to all subsequent pawns. The core treatment effects are robust to any of these ways of handling repeat pawning.  }

%\textit{Do file: } \texttt{multiple\_loans.do}
\end{table}

\end{landscape}

\begin{figure}[!htb]
    \caption{Determinants of choice}
    \label{determinants_choose}
    \begin{center}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
    \end{subfigure}
    \end{center}
      \legend{  The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment. Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm. }
%\textit{Do file: } \texttt{determinants_choice.do}       
\end{figure}

\vspace{.2in}
\begin{figure}[!htb]
    \caption{Histogram of payments}
    \label{hist_payments}
    \begin{center}
    \begin{subfigure}{0.32\textwidth}
        \caption{Status-quo}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
    \end{subfigure}
    \begin{subfigure}{0.32\textwidth}
        \caption{Forced commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
    \end{subfigure}
    \begin{subfigure}{0.32\textwidth}
        \caption{Choice commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
    \end{subfigure}    
    \end{center}
     \legend{ This figure shows the schedule of payments for each treatment arm. In other words it records the time after the loan origination when the borrower makes a payment toward recovery of the pawn. We can see that for both the Forced commitment and Choice commitment arm, payments are bunching at the 30 and 60 days, while most payments are done around the due date of the loan (90 days).}

      %\footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
\end{figure}

@@

Some loans in our sample are ``censored'' in that they continue beyond our observation period.
For these loans, we do not know whether the borrower ultimately defaulted or recovered her pawn.
In this appendix, we show that our main results are robust to different ways of addressing censoring.

Our main results, presented above, make no assumption on the default/recovery status of this loans. However, we compute the Financial Cost \& APR considering all the payments done so far. We now consider some alternative approaches. \\

One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.  In Table \ref{bounding_censoring} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.  Panel A assumes all censored loans are repaid, and Panel D that all default. Because forced commitment causes borrowers to make payments earlier than they otherwise would have, In Panel A we make a conservative assumption. To see why, suppose for the sake of argument that commitment affects payment timing, but does not not default.
In other words, suppose that treatment makes censoring \emph{less likely} but has no effect on uncensored outcomes. 
If we were to treat all outstanding loans as defaults--the opposite of our convention--this would artificially inflate the rate of default among control loans relative to treatment loans.

Panel B provides the lower bound for the treatment effect by assuming censored control loans are always repaid and treatment loans never are, and Panel C the upper bound by making the reverse assumption.  Comfortingly, even with these extreme assumptions the significance on the main treatment effects never flips and treatment effects on financial cost and interests payments remain negative and significant in all scenarios.  So there appears to be no scope for the censoring issue to overturn our main results.

Finally, Panel E of this table conducts a lasso logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.  This is a best guess of the outcome on censored loans.  Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -204 (main results) to -264 (censored loans predicted), and the APR from -11\% to -17\%.  Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.

\begin{table}[!htb]
\caption{Bounding censoring} 
\label{bounding_censoring}
\begin{center}
\resizebox{0.9\textwidth}{!}{
\scriptsize{\input{./Tables/censoring_imp.tex}}
}
\end{center}

 \legend{  Given the censored loans, i.e. loans that have not finished by the end of the observation period, we estimate `a la Manski' bounds for these loans, meaning that we impute all loans to either \emph{default}$=1$ or \emph{recovery}$=0$ depending on the treatment arm. Different panels perform different imputations for the censored loans for all possible combinations for the imputation, and computes the ATE for the same outcomes of Table \ref{main_impact_table}. Panel A, for instance, assumes that all outstanding loans are fully payed. Panel B is the most conservative imputation since it assumes all outstanding loans in the control arm are payed, while all the outstanding loans in the forced commitment arm default. Panel C, on the other hand, is the most optimistic scenario opposite to that of Panel B. Panel D assumes all remaining loans default. The last panel makes the imputation to the censored loans according to the best prediction using a piecewise lasso logit model for default. In concrete, we build two logit models with lasso regularization, depending whether the loan duration is less than 220 days (two cycles) or more than 220 days. For prediction we use the former whenever the last recorded payment was done within 220 days, and the latter otherwise. Both models includes loan characteristics (loan size, branch), and payment behavior (loan duration so far, days to first payment, \% of first payment, \% of payments at 30, 60, 90, and 105 days, and \% of interest payed at 105 days), but the latter model also includes \% of payments at 150, 180, and 210 days. This predictive model achieves an accuracy rate of 92\% both in-sample and out-of-sample.
 Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome. }
 \end{table}

\begin{figure}[!htb]
        \caption{Interpolation on bounding censoring}
    \label{interpolation_censoring_imp}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
   \caption{Significance area for APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
    \end{subfigure}     
    \begin{subfigure}{0.49\textwidth}
   \caption{Significance area for Default }
        \centering
        \includegraphics[width=\textwidth]{Figuras/frontera_sig_def_imp.pdf}
    \end{subfigure} 
    \end{center}
     \legend{  The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
     This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment. Each corner in the square will correspond to one of the panels from the Table \ref{bounding_censoring}. For instance, the origin is the best-case scenario (Panel C) and the point (100,100) (Panel B) is the worst-case scenario. Thus we can think of this graph as an `interpolation' from the four extreme cases. The `x' indicates the proportions imputed by the lasso logit model, and the different lines correspond to setting different significance levels. We do not include the plot for financial cost, since for any imputation we still have significant results.}

     %\textit{Do file: }  \texttt{interpolation_censoring_imp.do}
\end{figure}

\begin{figure}[!htb]
        \caption{Survival graph}
    \label{survival_graph}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
   \caption{Ended contract}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
   \caption{Recovery}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
    \end{subfigure}     
    \end{center}
     \legend{  This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.}
     %\textit{Do file: }  \texttt{survival\_graph.do}
\end{figure}

>>>>

\title{ONLINE APPENDIX: The controlled choice design and private paternalism in pawnshop borrowing}
\runtitle{The controlled choice design and private paternalism}

@@

%\section{ Treatment Explanation Materials and Pictures}
\section{Additional materials} 
%\vspace{.2in}
\begin{figure}[!h]

    \begin{center}
    \begin{subfigure}{0.35\textwidth}
        \caption{Elapsed days to first payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \caption{Elapsed days to last payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
    \end{subfigure}
        \begin{subfigure}{0.35\textwidth}
        \caption{Payments as \% of loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
    \end{subfigure}
    \end{center}
        \caption{Behavior of borrowers who lost their pawn. This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn. Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment. Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan. This amounts to starting a new loan with the same conditions and same pawn. Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.}
        \label{proxy_naive}
      %\textit{Do file: }  \texttt{hist\_den\_default.do}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{ Internal Validity}

\begin{table}[!h]
\caption{Summary statistics and Balance}
\label{SS}
\begin{center}
\resizebox{0.65\textwidth}{!}{
\scriptsize{\input{./Tables/SS.tex}}
}
\end{center}
\legend {This table has two panels. Panel A uses administrative data at the loan level, while Panel B uses survey data. Each row in this table corresponds to a regression, where the level of observation is the individual loan originated. The dependent variables of these regressions are displayed in the first column. Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice). The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients. The admin data was a very limited set of pre-determined variables. The dependent variables in Panel A are the loan amount in pesos, and an indicator for whether the day of the loan origination was a weekday (as opposed to weekend). The dependent variables in Panel B from the survey. Subjective value of the pawn (how much would the client be willing to sell it for (Q3), an indicator for having trouble paying bills in the last 6-months (Q28), present bias (constructed from questions Q10 and Q29 in the standard way as in \cite{Ashraf}), an indicator for whether they make expenses budget for the month ahead of time. The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn), pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$) age is in year, +High-school is a dummy that indicates if the client has completed high school. 
}
%\textit{Do file: } \texttt{ss\_att.do}
\end{table}

If potential borrowers disliked being forced into a commitment contract, we would expect a lower number of pawns on branch days where only the commitment contract is available compared to control days. Table \ref{attrition_table} shows that this is not the case. There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day. Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability. Differences across arms are smaller when for medians, or when we compare the number of borrowers pawning (some borrowers pawn more than one piece). 
% Figure \ref{boxplot_attrition} shows that distribution of loans per day is comparable across arms. The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns becomes identical across arms.}

\begin{table}
\caption{Limited and balanced attrition}
\label{attrition_table}
\begin{center}
\scriptsize{\input{./Tables/Attrition.tex}}
\end{center}
\legend{Each row in this table 
 corresponds to a regression. The dependent variables are: the number of pawns-loans originated per day per branch, the number of borrowers per day-branch, a variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning, and an indicator of whether the person that obtained the loan answered the baseline survey. Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice). The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients. %Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.
 }
%\textit{Do file: } \texttt{ss\_att.do}
\end{table}

The bottom panel of Table \ref{attrition_table} shows balance in a more focused way, given that the surveys were conducted prior to the revelation of treatment status. We find that in no arm did more than three percent of individuals who responded to the survey go on to refuse loans. That is, the overwhelming marjority of potential borrowers did not leave the branch after learning which contract was on offer. Moreover, the extremely small fraction that did leave is balanced across arms.  Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.

A less critical form of attrition is differential refusal to answer the survey questions.  The survey was conducted before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.  Our core experimental estimates do not use the survey data as covariates, but the analysis in Section \ref{Paternalism} is restricted to the subset of borrowers who answered at least some survey questions. The bottom row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 78 percent).

%We now present an analysis of the extent to which the survey-responding sample is representative and balanced. Table \ref{SS_cond_survet} presents information about survey non-response. Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to at least one survey question. The p-values in the fourth column are for the F-test of no difference of means across treatment arms. Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rates across treatment arms. This panel uses data from participants who answered at least one survey question and went on to pawn on the same day as their survey response. From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are likewise stable across treatment arms.

% Table \ref{TUT_cond_survet} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
% The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
% In each row, column (1) presents the full-sample TUT estimate and standard error while the remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
% For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex. 
% As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
% In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
% For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
% In exercises that rely on a single survey question, we use data for every borrower who answered that question.
% In the random forest exercises described below, we use data for every borrower who answered at least one survey question.

% \begin{table}[H]
% \caption{Survey Non-response: TUT estimates for respondents to each survey question.}
% \label{TUT_cond_survet}
% \begin{center}
% \scriptsize{\input{./Tables/tut_cond_survey.tex}}
% \end{center}
% \legend{Some borrowers did not respond to our survey; others only completed part of the survey.
% This table computes the TUT effect for a number of sub-groups by survey response, and compares them against the overall TUT effect.
% The top panel uses financial cost as the outcome variable, while the bottom panel uses APR.
% Each group is defined by the borrowers who responded to a particular \emph{subset} of the survey questions. 
% For example, column (4) computes TUT effects for the subgroup of borrowers who responded to the two questions needed to compute our measure of present bias, while column (8) computes the TUT for the subgroup of borrowers who provided their age.
% The bottom row of the table counts the number of borrowers in each category.
% TUT estimates are quite stable across sub-groups and generally similar to the full-sample estimates.
% Because standard errors increase as sample size falls, some of the sub-group estimates are not statistically significant.}
% %\textit{Do file: } \texttt{tut_cond_survey.do}
% \end{table}

\section{ Main treatment effects: Additional material}

\begin{figure}[H]

    \begin{center}
    \begin{subfigure}{0.6\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
    \end{subfigure}
    \end{center}
\caption{Determinants of choice. The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment. Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm. }
    \label{determinants_choose}
%\textit{Do file: } \texttt{determinants_choice.do}       
\end{figure}

\subsection{Intermediate Outcomes}

\begin{landscape}

\begin{table}[!h]
\caption{Effects on intermediate outcomes}
\label{mechanisms}
\begin{center}

\scriptsize{\input{./Tables/mechanism.tex}}

\end{center}
\legend{This table explores treatment effects in ``intermediate variables''. Each column represents regression output for different dependent variables following equation (\ref{basic_reg}). Panel A focuses on variables related to the speed of payment. While Panel B focuses on variables related to default, and Panel C related to visits. 
% The outcome variables are as follows:  number of days elapsed between origination and first payment (col 1); percentage of the loan paid in the first payment (col 2); probability of recovery in the first visit (col 3); loan duration is the number of days the borrower took to payoff her loan for those that recover, the number of days until default for those that default, and the maximum number of days we observe them in the sample for those that have not recovered or defaulted (col 4); loan duration conditional on recovery; an indicator for paying a positive amount towards recovery but nonetheless losing the pawn (col 6); the percentage or the loan paid, conditional on defaulting --`wasted payments' (col 7). Column 8 uses the phrase `selling the pawn' for a dummy variable indicating the borrower did not pay any amount towards recovery and lost the pawn. Moreover, (col 9) shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. The dependent variable in column 10 is the number of day-visits to the branch (measured by the existence of transactions that day associated with our particular pawn), while column 11 conditions on borrowers that lost the pawn.
Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.}
%\textit{Do file: } \texttt{mechanisms.do}
\end{table}
\end{landscape}

@@

Some loans in our sample are ``censored'' in that they continue beyond our observation period.  For these loans, we do not know whether the borrower ultimately defaulted or recovered her pawn.   We have also shown that one effect of the forcing arm is to accelerate repayment, meaning that it is less likely for loans in this arm to be censored.  This issue is illustrated in Figure \ref{survival_graph}, which shows the CDF of loan completion (either default or recovery in Panel (a)) and loan recovery (Panel (b)) by the number of days since first pawn.  Two features of these graphs are salient for our analysis.  The first is the extent to which loan outcomes are observed more quickly in the forced commitment arm.  This is primarily due to the substantially higher rate of repayment of Forced Commitment loans at 120 days (15 pp higher than the other arms).  The second is the very low rate at which loans are recovered in any arm after 120 days.  In the 180-320 day window loans are largely dormant, suggesting that many of the censored loans will in fact end in default.

The confluence of censoring and a treatment effect on censoring is potentially problematic from an experimental point of view.  The approach taken in the headline results is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into the that treatment decreasing default.  Nonetheless, to be certain that this issue is not driving our results we conduct a bounding exercise to understand how large the effects of this problem can possibly be.

One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring. In Table \ref{bounding_censoring} we compare the Forced and Control arms, bounding the censoring issue by reversing assumptions about the outcome of censored loans in the treatment versus the control.   Panel B provides the lower bound for the treatment effect (closest to zero) by assuming censored control loans are always repaid and treatment loans never are; even in this lower-bound case the treatment effect is cost-reducing and significant at the 1\% significance level and indeed the magnitude of this lower bound estimate is only 6\% closer to zero than our headline result.   Panel C estimates the upper bound by making the reverse assumption.  Comfortingly, even with these extreme assumptions the significance on the main treatment effects never flips and treatment effects on financial cost and interests payments remain negative and significant in all scenarios.  So there appears to be no scope for the censoring issue to overturn our main results.

Finally, Panel E of this table conducts a logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.  This is a ``best guess'' of the outcome on censored loans.  Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -204 (main results) to -264 (censored loans predicted), and the APR from -11\% to -17\%.  Hence, while the censoring issue does have an effect on the magnitude of our estimated treatment effects, these  checks confirm that (a) the core results are fully robust to censoring, and (b) the headline approach that we take to the issue is conservative and likely understates the true magnitude of impacts.

\begin{table}[H]
\caption{Bounding censoring} 
\label{bounding_censoring}
\begin{center}
\resizebox{0.75\textwidth}{!}{
\scriptsize{\input{./Tables/censoring_imp.tex}}
}
\end{center}

 \legend{ Given the censored loans, i.e. loans that have not finished by the end of the observation period, we estimate `a la Manski' bounds for these loans, meaning that we impute all loans to either \emph{default}$=1$ or \emph{recovery}$=0$ depending on the treatment arm. Different panels perform different imputations for the censored loans for all possible combinations for the imputation, and computes the ATE for the same outcomes of Table \ref{main_impact_table}. Panel A, for instance, assumes that all outstanding loans are fully payed. Panel B is the most conservative imputation since it assumes all outstanding loans in the control arm are payed, while all the outstanding loans in the forced commitment arm default. Panel C, on the other hand, is the most optimistic scenario opposite to that of Panel B. Panel D assumes all remaining loans default. The last panel makes the imputation to the censored loans according to the best prediction using a piecewise lasso logit model for default. In concrete, we build two logit models with lasso regularization, depending whether the loan duration is less than 220 days (two cycles) or more than 220 days. For prediction we use the former whenever the last recorded payment was done within 220 days, and the latter otherwise. Both models includes loan characteristics (loan size, branch), and payment behavior (loan duration so far, days to first payment, \% of first payment, \% of payments at 30, 60, 90, and 105 days, and \% of interest payed at 105 days), but the latter model also includes \% of payments at 150, 180, and 210 days. This predictive model achieves an accuracy rate of 92\% both in-sample and out-of-sample.
 Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome. }

% \begin{figure}[H]

%     \begin{center}
%    % \begin{subfigure}{0.49\textwidth}
%    % \caption{Significance area for APR}
%    %      \centering
%    %      \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
%    %  \end{subfigure}     
%    %  \begin{subfigure}{0.49\textwidth}
%    % \caption{Significance area for Default }
%         \centering
%         \includegraphics[width=0.5\textwidth]{Figuras/frontera_sig_def_imp.pdf}
%     % \end{subfigure} 
%     \end{center}
%  \caption{Interpolation on bounding censoring for Default. This figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
%      This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment. Each corner in the square will correspond to one of the panels from the Table \ref{bounding_censoring}. For instance, the origin is the best-case scenario (Panel C) and the point (100,100) (Panel B) is the worst-case scenario. Thus we can think of this graph as an `interpolation' from the four extreme cases. The `x' indicates the proportions imputed by the lasso logit model, and the different lines correspond to setting different significance levels. We do not include the plot for APR nor financial cost, since for any imputation we still have significant results.}
%  \label{interpolation_censoring_imp}
%      %\textit{Do file: }  \texttt{interpolation_censoring_imp.do}
% \end{figure}

\begin{figure}[H]
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
   \caption{Ended contract}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
   \caption{Recovery}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
    \end{subfigure}     
    \end{center}
      \caption{Survival graph. This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.}
      \label{survival_graph}
     %\textit{Do file: }  \texttt{survival\_graph.do}
\end{figure}
